Additional analysis

### 2019-03-14 README.Rmd
Oops, fix data URL

>>>>

## Data

This project includes the following data files:

- [`data/raw_data/crackdowns_philanthropy_raw.csv`](data/raw_data/crackdowns_philanthropy_raw.csv): Original results from the Qualtrics survey
- [`data/derived_data/results_clean.csv`](data/derived_data/results_clean.csv): Final version of the data, cleaned with [`analysis/01_clean-data.Rmd`](analysis/01_clean-data.Rmd)
- [`data/derived_data/results_clean.yaml`](data/derived_data/results_clean.yaml): [YAML metadata](https://csvy.org/) describing the syntax of the cleaned data
- [`data/derived_data/results_clean.rds`](data/derived_data/results_clean.rds): `.rds` version of cleaned data
- [`data/derived_data/codes_to_exclude.csv`](data/derived_data/codes_to_exclude.csv): Unique IDs of participants who failed the attention checks or took the survey outside of Mechanical Turk. These are excluded from the final data in [`analysis/01_clean-data.Rmd`](analysis/01_clean-data.Rmd)
- [`raw_data/ipums-cps/`](raw_data/ipums-cps/): Data extracts from the US Census's Current Population Survey (CPS) via the [Minnesota Population Center's Integrated Public Use Microdata Series (IPUMS)](https://cps.ipums.org/cps/):
    -  `cps_2017.dat.gz`: 2017 ASEC, with the following variables selected (in addition to whatever IPUMS preselects by default) (and weighted by `ASECWT`):
        - `AGE`
        - `SEX`
        - `EDUC`
        - `INCTOT`
    -  `cps_09_2015.dat.gz`: September 2015 basic monthly CPS (which includes the Volunteer Supplement), with the following variables selected (and weighted by `VLSUPPWT`):
        - `VLSTATUS`
        - `VLDONATE`
